Approximate State Abstraction

### 2016-01-30 paper/paper.tex
Lemma 1 proof all done -- needs a good formatting though

Consider the following policy on states in $\mathcal{S}_G$:
\begin{equation}
\pi_{A,t}(s)=
\begin{cases}
\pi_G^*(s), \text{if $t<=0$}\\
\pi_A^*(\ep(s)), \text{if $t > 0$}\\
\end{cases}
\end{equation}

Again, consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$

\begin{align*}
\text{Let }V^{\pi_{A,t}}(s_G) &= \\
&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
\end{align*}

where $g, g' \in \mathcal{S}_G$.

%Start induction on following the optimal abstract policy
We now show by induction on $t$ that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so it trivially follows that
\begin{equation}
V^{\pi^*}(s_G) \leq V^{\pi_{A,0}}(s_G) + \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

@@

By definition 
\begin{align*}
&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
&\text{Applying our inductive hypothesis yields}\\
&V^{\pi_{A,t}}(g, a) \geq\\
&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
&\text{Applying Equation \ref{eq:Q*OptActionResult} yields}\\
&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
& \text{Thus,}\\
&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{align*}

From our base case and induction we conclude that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

Thus we conclude,
\begin{equation*}
\forall_{g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A}^*}(g) + \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

\begin{equation*}
\forall_{g \in \mathcal{S}_g} \left | V^{\pi^*}(g) - V^{\pi_{A}^*}(g) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

>>>>

Consider the policy for $M_G$ of following the optimal abstract policy $\pi^*_A$ for t steps and then following the optimal ground policy $\pi^*_G$ in $M_G$:

\begin{equation}
\pi_{A,t}(s)=
\begin{cases}
\pi_G^*(s), \text{if $t<=0$}\\
\pi_A^*(\ep(s)), \text{if $t > 0$}\\
\end{cases}
\end{equation}

For a particular $t$, the value of this policy for $s_G \in \mathcal{S}_G$ is as follows:
\begin{align*}
V^{\pi_{A,t}}(s_G) &= \\
&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}' \in \mathcal{S}_G}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
\end{align*}

%Start induction on following the optimal abstract policy
We now show by induction on $t$ that
\begin{equation}
\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so our bound trivially holds in this case.

@@

Consider a fixed but arbitrary state in $\mathcal{S}_G$, $s_G$.

@@

By definition 
\begin{align*}
&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
&\text{Applying our inductive hypothesis yields}\\
&V^{\pi_{A,t}}(g, a) \geq\\
&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
&\text{Applying Equation \ref{eq:Q*Claim2} yields}\\
&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
& \text{Thus,}\\
&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{align*}

Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.

Thus, our base case and induction we conclude that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

Thus, we conclude
\begin{equation*}
\forall_{s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A}^*}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

\begin{equation*}
\forall_{s_G \in \mathcal{S}_g} \left | V^{\pi^*}(s_G) - V^{\pi_{A}^*}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}
